\section{Conclusions}
We have proposed a robust approach to linear regression models with
censored observations based on the scale mixtures of normal
distributions, called the \textrm{SMN-CR} models. This offers a
great deal of flexibility in dealing with censored data in the
presence of outliers.  A novel ECME algorithm to obtain approximated
ML estimates is developed by exploring the statistical properties of
the truncated SMN distributions. Our proposed algorithm has a
closed-form expression for the E-step, based on formulas for the
moments of the truncated SMN distribution. We applied our
methodology to a real data (freely downloadable from R) as well as
to simulated data to illustrate how the procedures can be used to
evaluate model assumptions, identify outliers, and obtain robust
parameter estimates.  From these results it is encouraging that the
use of \textrm{SMN-CR} models offer better fitting, better
protection against outliers and more precise inferences than their
normal counterparts.

Although the \textrm{SMN-CR} models considered here has shown great
flexibility to modeling symmetric data, its robustness against
outliers can be seriously affected by the presence of skewness.
Recently, \cite{Lachos_Ghosh_Arellano_2009}  proposed a remedy to
accommodate skewness and heavy-tailedness simultaneously, using
scale mixtures of skew-normal (SMSN) distributions. We conjecture
that our methodology can be used under CR models, and should yield
satisfactory results at the expense of additional complexity in
implementation. An in-depth investigation of such extensions is
beyond the scope of the present paper, but it is an interesting
topic for further research. Finally, the proposed EM-type algorithm
has been coded and implemented in the R package \emph{SMNCensReg},
which is available for download at CRAN repository.
